%\appendix

\chapter{Spoken Tutorial based SELF workshop on Oscad}
\section{What is SELF Workshop?}

The Spoken Tutorial project is about teaching and learning a particular FOSS (Free and Open Source Software) like Linux, Scilab, LaTeX, PHP \& MySQL, Java, C/C++, LibreOffice, Oscad etc. via an easy video tool- Spoken Tutorials. Some of the salient features of SELF (Spoken Tutorial based Education and Learning through Free FOSS study) workshops are -
\begin{itemize}
\item This method is highly conducive to self learning. Once one get started any student or faculty can master the FOSS.
\item UG, PG or research scholar students and even teachers of Science, IT, Engineering, Commerce, Management disciplines can learn any of the FOSS.
\item The training workshops are conducted remotely via a video conferencing tool (Skype). Typically, the first workshop at any college is of 2 hour duration.
\end{itemize}

\section{What do we offer in Oscad workshops?}

\begin{itemize}
\item Ubuntu Linux live CD with Oscad software and Spoken Tutorials on Oscad, KiCad and Ngspice.
\item Instruction sheet to practice all tutorials.
\end{itemize}

\section{What is expected from the organizing institute}

\begin{enumerate}
\item To start of, any college which is organizing the workshop needs to get a computer lab ready with machines that support sound with Internet  connectivity.
\item One computer per user, with audio/video functionality and DVD drive in working condition is required.
\item One Headphone per user is required.
\item There is no lower or upper limit on the number of participants. This just depends on the number of computers available.
\item For additional participants, laptops if available can be used.
\item The main organizer's computer should have a webcam via which Spoken Tutorial team can monitor the workshop.
\item On a convenient day, participants take an assessment test and on clearing it get certificates from Spoken Tutorial project, IIT Bombay.
\end{enumerate}


\textbf{Useful Links}
\begin{enumerate}
\item Spoken Tutorials: http://spoken-tutorial.org
\item Oscad: http://oscad.net
\item FOSSEE project: http://fossee.in
\end{enumerate}

\textbf{Contact}

For Spoken Tutorial related queries please write to: {\tt contact@spoken-tutorial.org}\\
To contribute to Oscad project OR to know more about Oscad project: {\tt info@fossee.in}
